The SMT Competition 2015--2018

### 2019-08-21 2018/report/SMT-COMP.tex
Clarify discussion of MathSAT/Z3 performance and industrial relevance

Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
highest-ranked solvers for all (competitive and non-competitive) division from
2015--2018.
We include solvers that were running hors concours (and hence non-competing
and ineligible to be recognized as official competition winners).
Non-com-petitive divisions use gray font.
Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
but non-competing solver $B$ actually ranked best if non-competing solvers
were taken into consideration.
Entries
$A/B$ indicate that solver~$A$ ranked first considering sequential
performance, while~$B$ ranked first considering parallel performance.
When the same solver ranked first in both, which is most often the
case, its name appears just once.
Table cell colors (other than white) indicate the best competing sequential
solver performance, no cell color indicates that the best sequential solver
performance was by a non-competing solver and no competing solvers participated
in that division.
Full division rankings are available from the competition website.

It is interesting to note that the non-competitive solvers MathSAT and Z3 often appear as the best performing solver. We do not see this as detracting from the overall significance of results. Both solvers are industrial-strength tools, actively maintained and tuned. The reasons for non-entry into the competition are orthogonal to their suitability for the competition. Indeed, Z3 has been entered into the competition competitively in the past and one can assume that it was trained on the current problems (as much as any solver is). Finally, the fact that industrial-strength solvers perform well in the competition supports the notion that the benchmarks in the competition are industrially relevant.

>>>>

Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
highest-ranked solvers for all (competitive and non-competitive) division from
2015--2018.
We include solvers that were running hors concours (and hence non-competing
and ineligible to be recognized as official competition winners).
Non-com-petitive divisions use gray font.
Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
but non-competing solver $B$ actually ranked best if non-competing solvers
were taken into consideration.
Entries
$A/B$ indicate that solver~$A$ ranked first considering sequential
performance, while~$B$ ranked first considering parallel performance.
When the same solver ranked first in both, which is most often the
case, its name appears just once.
Table cell colors (other than white) indicate the best competing sequential
solver performance; no cell color indicates that the best sequential solver
performance was by a non-competing solver and no competing solvers participated
in that division.
Full division rankings are available from the competition website.

It is interesting to note that the non-competing solvers MathSAT and
Z3 often appear as the best performing solver.  We view this as
confirmation of the industrial significance of competition results.
Both solvers are industrial-strength tools, actively maintained and
tuned.  The reasons for non-entry into the competition are orthogonal
to their suitability for the competition.  Indeed, Z3 has been entered
into the competition competitively in the past, and one can assume
that it was trained on the current problems.  The fact that
industrial-strength solvers perform well in the competition supports
the notion that the benchmarks in the competition are industrially
relevant.
